Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-15 Draft/shower.tex
edit shower.tex

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline\hline
        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+XX}_{-YY} {}^{+XX}_{-YY} $ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.368$ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0.0}_{-1.0}$ & $0.0006$  \\
        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
    \end{tabular}
    \caption{\label{tab:PSratesNLO} Rates at NLO-QCD  accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties is shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
are respectively the nine-point scale uncertainty and the PDF one. Theory uncertainties are in percent.}
\end{table}

We now present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
\ref{tab:PSratesNLO}, at LO and NLO
accuracy respectively. For {\sc MG5\_aMC}, 
the numbers whith $\Gamma_{\rm resc}$ are rescaled to 
take into account the width effects described in the above paragraph.d  At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}, we also quote
theoretical uncertainties: for the former, we show both PDF and scale uncertainties, obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
scale by a factor 2 around its central value, Eq.~\ref{eq:defscale} (nine-point variations); for the latter, we show the 
three-point scale uncertainties, obtained by considering correlated variations of the renormalization and factorization scales. 
We observe that, once the width effect is taken into
account, total rates from different tools agree within few per cent. Larger discrepancies however will appear for differential observables, which we are going to discuss in
the following. For any observable, results will be presented in two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
{\sc VBFNLO} \emph{i.e.}\ the VBS approximation with $s$-channel contributions). For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above. As for the table, we show theoretical uncertainties for the NLO+PS samples
obtained with {\sc VBFNLO} and {\sc MG5\_aMC}: 
again, for the first the band corresponds to three-point variations, while for the second the darker (lighter) band corresponds to nine-point 
scale variations (plus PDF uncertainties, linearly added).

>>>>

\begin{table}[h!]
    \centering
    \begin{tabular}{c|r@{ $\pm$ }l}
      Code  &  \multicolumn{2}{c}{$\sigma[\rm{fb}]$}  \\
        \hline\hline
        {\sc MG5\_aMC}+{\sc Pythia8}&  $1.450 ^{+2\%}_{-1\%} {}^{+5\%}_{-6\%} $ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}&  $1.445 $ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Pythia8}, $\Gamma_{\rm resc}$&  $1.368$ & $0.004$  \\
        {\sc MG5\_aMC}+{\sc Herwig++}, $\Gamma_{\rm resc}$&  $1.363$ & $0.004$  \\
        {\sc POWHEG}  &  $1.3642$ & $0.0004$  \\
        {\sc VBFNLO}+{\sc Herwig7-Dipole} &  $1.3389 ^{+0\%}_{-1\%}$ & $0.0006$  \\
        {\sc VBFNLO}+{\sc Herwig7-Default} &  $1.3067$ & $0.0006$  \\
    \end{tabular}
    \caption{\label{tab:PSratesNLO} Rates at NLO-QCD  accuracy matched to parton shower within VBS cuts obtained with the different codes used in this comparison,
    for the ${\rm p}{\rm p}\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}{\rm j}{\rm j}$ process. The {\sc MG5\_aMC} results with $\Gamma_{\rm resc}$ 
    are rescaled to account for the effect related to the boson widths computed by {\sc MadSpin} (see the text for details). For
    {\sc VBFNLO}+{\sc Herwig7-Dipole}, the three-point scale uncertainties is shown, while for  {\sc MG5\_aMC}+{\sc Pythia8} the two displayed uncertainties
are respectively the nine-point scale uncertainty and the PDF one.}
\end{table}

We now present the results of predictions matched to parton shower: the total rates within VBS cuts are displayed in Tables~\ref{tab:PSratesLO} and
\ref{tab:PSratesNLO}, at LO and NLO
accuracy respectively. For {\sc MG5\_aMC}, 
the numbers whith $\Gamma_{\rm resc}$ are rescaled to 
take into account the width effects described in the above paragraph.d  At NLO accuracy, for {\sc MG5\_aMC} + {\sc Pythia8} and {\sc VBFNLO}-{\sc Dipole}, we also quote
theoretical uncertainties: for the former, we show both PDF and scale uncertainties, obtained via exact reweighting~\cite{Frederix:2011ss} by varying independently the renormalization and factorization
scale by a factor 2 around its central value, Eq.~\ref{eq:defscale} (nine-point variations); for the latter, we show the 
three-point scale uncertainties, obtained by considering correlated variations of the renormalization and factorization scales. 
We observe that, once the width effect is taken into
account, total rates from different tools agree within few per cent, both at LO and NLO. Larger discrepancies however will appear for differential observables, which we are going to discuss in
the following. Before turning to the differential observables, we point out the smallness of the theory uncertainties due to the scale variations, both when
scales are varied independently and when they are varied in a correlated manner. On the other hand PDF uncertainties are larger, at the level of 
$\pm 5\%$. Concerning differential kinematic distributions, for each observable we will display results two plots, shown side-by-side. In the plot on the left (right), (N)LO+PS predictions are shown
with different colours in the main frame. In the inset, these predictions are compared in both cases with a fixed-order prediction at NLO accuracy (obtained with
{\sc VBFNLO} \emph{i.e.}\ the VBS approximation with $s$-channel contributions). For the differential observables, the {\sc MG5\_aMC} predictions are \emph{not} rescaled to compensate for the width effect mentioned above. As for the table, we show theoretical uncertainties for the NLO+PS samples
obtained with {\sc VBFNLO} and {\sc MG5\_aMC}: 
again, for the first the band corresponds to three-point variations, while for the second the darker (lighter) band corresponds to nine-point 
scale variations (plus PDF uncertainties, linearly added).
